---
title: "Simple document"
output: github_document
    
---

I'm an R Markdown document! yes

# Section 1

Here's a _aaa_ that samples from 
a _normal distribution_:

```{r eval=TRUE}
samp = rnorm(100)
length(samp)
```

# Section 2

#I can take the mean of the sample, too! The mean is `r mean(samp)`.
```{r learning_assignment_1}
library(tidyverse)
plot_df=
    tibble(
      x=rnorm(1000, mean=1, sd=0.5),
      y=1+2*x+rnorm(1000)
    )
ggplot(plot_df, aes(x=x,y=y))+geom_point()
```

```{r}
```{r learning_assessment_1}
library(tidyverse)

la_df = tibble(
  norm_samp = rnorm(500, mean = 1),
  norm_samp_pos = norm_samp > 0,
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + 
    geom_histogram()

median_samp = median(pull(la_df, norm_samp))
```

The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell


